\textbf{Towards File System integrity verification in BTRFS}

### 2019-08-02 paper.tex
Extent section about the verification algorithm.

\documentclass[10pt]{article}
%\documentclass[10pt,twocolumn]{article}
\usepackage[a4paper]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titling}
\usepackage{graphicx}

@@

\subsection{File System Verification}
If the ``plain'' HMAC approach will be taken, the next step after the inclusion
of the XXHASH64 patchset will be implementing a new mount option, which
queries the Linux Kernel's internal keyring for a key which will be used to
create the HMACs. Also the respective HMAC function needs to be enabled in
BTRFS and the user-space code needs to be adopted for this as well.

>>>>

\documentclass[10pt]{article}
%\documentclass[10pt,twocolumn]{article}
\usepackage[a4paper]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\subsection{File System Verification}
If the ``plain'' HMAC approach will be taken, the next step after the
inclusion of the XXHASH64 patchset will be implementing a new mount option,
which queries the Linux Kernel's internal keyring for a key which will be used
to create the HMACs upon mount time. Also the respective HMAC function needs
to be enabled in BTRFS and the user-space code needs to be adopted for this as
well.\\

For ever data block $b$ and a given key $K$ an HMAC is calculated according to
the following formula:
\[
HMAC(K,b) = H((K' \oplus opad) || H((K' \oplus ipad)|| b ))
\]
\[
K =
\begin{cases}
	H(K) & \text{if } K \text{is larger than the hash blocksize} \\
	K & \text{otherwise}
\end{cases}
\]
With $opad$ and $ipad$ being the defined outer and inner paddings defined by
the HMAC RFC. These values will be saved in the File System's Checksum tree
for each data block. The internal on-disk structure's will use the above
formula for their checksum values stored in \texttt{struct btrfs\_header}.\\

If a data block has been modified, without the modifier having access to the
HMAC key $K$ a read of this data block will be rejected by the File System's
end-io hooks for the Page Cache's \texttt{readpage()} method and an error
message will be printed to the Kernel's log. The same will happen for disk
blocks representing File System internal meta-data. Despite it's name the
\texttt{\_\_readpage\_endio\_check()} function also gets called when the Page
Cache is avoided, like in the case of Direct-IO and thus the integrity and
authenticity of the data is guaranteed as well.
